Title

### 2014-01-11 paper/parts/results.tex
Added log-log plot of the distribution of community sizes.

\subsection{Comparing Community-Types with Normalized Mutual Information}

>>>>

\begin{figure}[h!]
  \centering
\includegraphics[width=0.50\textwidth]{Figures/comm_sizes_ecdf_loglog.pdf}
\caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
\label{Fig-community_size_distribution}
\end{figure}

\subsection{Comparing Community Types with Normalized Mutual Information}
